---
title: "Voting and Postcards"
author: "Eric Butte"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
```


```{r}
x <- shaming |> 
  mutate(civ_engage = primary_00 + primary_02 + primary_04 + 
                      general_00 + general_02 + general_04) |> 
  select(primary_06, treatment, sex, age, civ_engage) |>
  mutate(voter_class = case_when(
    civ_engage %in% c(5, 6) ~ "Always Vote",
    civ_engage %in% c(3, 4) ~ "Sometimes Vote",
    civ_engage %in% c(1, 2) ~ "Rarely Vote"
  ),
  voter_class = factor(voter_class, levels = c("Rarely Vote", "Sometimes Vote", "Always Vote"), ordered = TRUE)) |>
  mutate(voted = as.factor(primary_06))
```

$$
\hat{Y}_i = \beta_0 + \beta_1 \cdot \text{treatment}_i + \beta_2 \cdot \text{sex}_i + \beta_3 \cdot \text{age}_i + \beta_4 \cdot \text{civ\_engage}_i
$$


$$
\text{logit}(\Pr(Y_i = 1)) = \beta_0 + \beta_1 \cdot \text{sim}_{1i} + \beta_2 \cdot \text{sim}_{2i} + \cdots + \beta_6 \cdot \text{sim}_{6i}
$$


```{r}
library(tibble)

model_summary <- tibble::tibble(
  term = c(
    "(Intercept)",
    "age",
    "sexMale",
    "treatmentCivic Duty",
    "treatmentHawthorne",
    "treatmentSelf",
    "treatmentNeighbors",
    "voter_classSometimes Vote",
    "voter_classAlways Vote",
    "treatmentCivic Duty:voter_classSometimes Vote"
  ),
  estimate = c(
    -2.434345037, 0.012087706, 0.035583881, 0.086052489, 0.070663507,
    0.202358812, 0.358818468, 0.819714170, 1.608953223, 0.030789566
  ),
  std_error = c(
    0.0219687863, 0.0002867168, 0.0075705445, 0.0444229420, 0.0452646335,
    0.0430280383, 0.0416393173, 0.0203450310, 0.0215576735, 0.0470730950
  ),
  statistic = c(
    -110.8092636, 42.1590509, 4.7003068, 1.9371182, 1.5611196,
    4.7029523, 8.6172995, 40.2906327, 74.6348265, 0.6540799
  ),
  p_value = c(
    0, 0, 2.59771e-06, 5.27309e-02, 0.1184955,
    2.564263e-06, 6.855166e-18, 0, 0, 0.5130603
  ),
  conf_low = c(
    -2.477540311, 0.011525794, 0.020745959, -0.001619693, -0.018697445,
    0.117501330, 0.276766195, 0.779980619, 1.566827493, -0.060959822
  ),
  conf_high = c(
    -2.39142174, 0.01264971, 0.05042202, 0.17253951, 0.15876293,
    0.28618923, 0.44000741, 0.85973464, 1.65133478, 0.12358568
  )
)

model_summary

```




Governor elections in the great state of Texas are a massive event. We will try and uncover patterns of human behavior that show why certain citizens voted for one candidate as opposed to another. A weakness in my model is trying to draw conclusions from michigan elections and apply them to texas elections. I modeled the impact of postcards on voter's decision for a political candidate as a logistic regression function of another election in AMerica. 
